
% A B S T R A C T

\pagestyle{empty}

\begin{latin}

\EnglishAbstractFont

\begin{center}
\textbf{abstract}
\end{center}

Many advantages of the Internet have turned it into one of the most popular ways to communicate and exchange ideas. Due to increasing data provided in the World Wide Web, accessing particular information, which matches user needs, becomes challenging. So we need to have some kinds of tools for managing access points and searching through this massive source of data. As a result, general software for searching through the Internet's data implemented. However, these general software don't fulfill users for special needs. For example, one of these needs is employment. As we know, there aren’t any efficient Persian search engines for finding proper work for applicants.
\\
This project, by using active Persian employment websites, develops an integrated search engine. In the middle, we need to extract employment advertisements and applicants resumes from these websites. In addition, we need to study successful English employment websites such as LinkedIn and extract their database schema for saving resumes. Finally, we enhance an open source search engine to extract Persian Employments advertisements efficiently. As a result, we get more accurate and robust search experience among these advertisements and decrease index size which is very important in large scale search engines.

\textbf{Keywords:} Advertisement, Search Engines, Nutch, Lucene, Data Mining

\end{latin}

\newpage
